An application of Graph Theory to MDAO problem formulation

### 2012-10-01 problem_formulation.tex
stuff

    Where $A,B,C$ represent analysis tools, $F,G1,G2,E,R$ are objective and constraint functions, and each analysis tool 
    has a set of input and output variables. While this does represent a complete problem formulation, some assumptions have
    inherently been made about the solution strategy. A coupling constraint, $E$, and $C$ is directly dependent
    $A.f$ and $B.f$ as it's inputs. This implies that first you must run $A$ and $B$, then $C$ and
    iterate on the design variables in $A$ and $B$ until you satisfy $E$. However, a different solution could be equally valid and still represent
    the same fundamental problem:

>>>>

    Where $A,B,C$ represent analysis tools, $F,G1,G2,E,R$ are objective and constraint functions, and each analysis tool 
    has a set of input and output variables. While this does represent a complete problem formulation, 
    it's not the fundamental one since some assumptions have inherently been made about the solution 
    strategy. $C$ is directly dependent
    $A.f$ and $B.f$ as it's inputs. This implies that first you must run $A$ and $B$, then $C$ and
    iterate on the design variables in $A$ and $B$ until you satisfy $E$. However, a different solution could be equally valid and still represent
    the same fundamental problem:
